---
title: "FARS Function Collection"
author: "Aziiz Sutrisno"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This `vignette` gives a brief overview to the **FARS** (Fatality Analysis Reporting System) using data from the [National Highway Traffic Safety Administration](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars). The dataset is a nationwide census providing the American public yearly data, regarding fatal injuries suffered in motor vehicle traffic crashes.

#` Load the Packages

```{r echo=FALSE, include=FALSE}

library(fars)
library(dplyr)
library(maps)

```

## Functions in this package

There are three functions for this package:
1.  `fars_read()` - This function works to read the NHTSA dataset and translate it into a required format
2.  `fars_read_years()` - This function works to filter the years in the dataset
3.  `fars_map_state()` - This function create a visualization of the 

## Examples of `fars_read()`

The function `fars_read()` reads dataset from a file path provided as an argument. It returns a `tibble` with loaded data:

```{r fars_read_example}
filename <- system.file("extdata/accident_2013.csv.bz2", package = "fars")
fars_read(filename)
```

## Using the Year Dataset that you need

This function takes a list of years for FARS dataset and convert it to the  tidy dataset with additional column of the year.

```{r fars_read_years_example}

years <- c(2013:2014)
filtered_data <- fars_read_years(years)

```


## Plot Fatal accident locations

This function `fars_map_state()` use the object class created by the `fars_read_years()` function as arguments and returns a plot of the state with accident locations. The state indices need to correspond available indeces from the dataset. Here are some examples:

```{r fars_map_state_example}
setwd(system.file("data", package = "fars"))
fars_map_state(45, 2015)
```
